---
title: "Evaluating all those forests to improve the geologic map"
author: "fabian gruber"
date: "October 19, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
require(e1071)
require(RCurl)
require(repmis)
require(randomForest)
proj2path="/media/fabs/Volume/01_PAPERZEUG/PROJECTP2/"
myfunctions <- getURL("https://raw.githubusercontent.com/fernstgruber/Rstuff/master/fabiansandrossitersfunctions.R", ssl.verifypeer = FALSE)
eval(parse(text = myfunctions))
load(paste(proj2path,"data2017/modeldata_sGUkartiert.RData",sep=""))
```
## 

Roughness 
```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"/data2017/temprdata/ranfor_fw_5fold_6p_SGU_kartiert_roughness/",sep=""),kk=1:5,endround = 6,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

Allpreds SBintern

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_SBintern_SGU_kartiert_allpreds/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

roughness SBintern

```{r}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_SBintern_SGU_kartiert_roughness/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```
Allpreds till (richtig vs falsch)

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_till_allpreds/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

Allpreds tillornot

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_tillornot_allpreds/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

roughness tillornot

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_tillornot_roughness/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

roughness till (richtig vs falsch)

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_till_roughness/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

Hier tillornot mit SGU_gk allpreds

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_tillornot_mitSGUgk_allpreds/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

tillornot mit SGU_gk roughness

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_tillornot_mitSGUgk_roughness/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

slopedeposits or not allpreds

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_SDornot_allpreds/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

slopedeposits or not roughness 

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_SDornot_roughness/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

slopedeposits or not rALLPREDS & SGU_gk

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_SDornot_mitSGUgk_allpreds/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```

slopedeposits or not roughness & SGU_gk

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(proj2path,"data2017/temprdata/ranfor_SDornot_mitSGUgk_roughness/",sep=""),kk=1:5,endround = 3,error = "cverror",geheim = "geheimerprederror",yrange=c(0,0.6))
```