---
title: "GEOeinheiten Parameterauswahl für 100pergeomorph"
author: "fabian gruber"
date: "April 24, 2017"
output: html_document
---
<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 22px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size:20px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 8px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

      
```{r,include=FALSE}
library(RCurl)
library(rgrass7)
library(repmis)
require(xtable)
require(e1071)
myfunctions <- getURL("https://raw.githubusercontent.com/fernstgruber/Rstuff/master/fabiansandrossitersfunctions.R", ssl.verifypeer = FALSE)
eval(parse(text = myfunctions))
source_data("https://github.com/fernstgruber/PROJECTP2/raw/master/data2017/classesandparamsets.RData")
base="/home/fabs/Data/paper2data/RDATA/"
source_data("https://github.com/fernstgruber/p2/blob/master/data2017/geotopodata_twohundredpergeomorph_2017.RData?raw=true")
twohundred <- modeldata
source_data("https://github.com/fernstgruber/p2/blob/master/data2017/modeldata_onehundredpergeomorph.RData?raw=true")
onehundred <- modeldata
rm(modeldata)
geolegendeng <- read.table(text=getURL("https://raw.githubusercontent.com/fernstgruber/p2/master/data2017/geolegendeng.txt"),sep="\t",header=T)
names(geolegendeng) <- c("geounit_eng","Abbrev.","short.description","geomorphologie_beschreibung","code")
geolegendeng <- geolegendeng[,c(2,1,3,4,5)]
```

##ALL TERRAIN 
### SVM n=100

```{r}
predict_radial_newlegend_fullparamset(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=1,altdata=twohundred,legend=geolegendeng)
```


```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_allterraincols_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full(modeldata=onehundred, dependent="geomorphologie_beschreibung", predictors=c("Channel_Network_Base_Level","slope_DTM_50m_avg_ws7","Texture","ChannelNetworkBaseLevel", "Modified_Catchment_Area","VerticalDistancetoChannelNetwork","Catchment_slope","Topographic_Wetness_Index","TPI_i0m_o400m","Convexity"),legend=geolegendeng,altdata=twohundred)
```

### SVM n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_allterraincols_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full(modeldata=twohundred, dependent="geomorphologie_beschreibung", predictors=c("Channel_Network_Base_Level","slope_DTM_50m_avg_ws7","Texture","ChannelNetworkBaseLevel", "Modified_Catchment_Area","VerticalDistancetoChannelNetwork","Catchment_slope","Topographic_Wetness_Index","TPI_i0m_o400m","Convexity"),legend=geolegendeng,altdata=onehundred)
```
### RandomForest n=100

```{r}
importance_ranfor_pset_newlegend(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=1,altdata=twohundred,legend=geolegendeng)
```

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_allterraincols_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full(modeldata =onehundred,dependent="geomorphologie_beschreibung",predictors=c("Channel_Network_Base_Level","slope_DTM_50m_avg_ws7","Texture","ChannelNetworkBaseLevel", "Catchment_Area2","VerticalDistancetoChannelNetwork","Convexity"),altdata=twohundred,legend=geolegendeng)
```


### RandomForest n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_allterraincols_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full(modeldata =twohundred,dependent="geomorphologie_beschreibung",predictors=c("Channel_Network_Base_Level","slope_DTM_50m_avg_ws7","Texture","ChannelNetworkBaseLevel", "Catchment_Area2","VerticalDistancetoChannelNetwork","Convexity"),altdata=onehundred,legend=geolegendeng)
```
##LOCAL TERRAIN 
###SVM n=100

```{r}
predict_radial_newlegend_fullparamset(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=2,altdata=twohundred,legend=geolegendeng)
```

```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_localterrain_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full(modeldata=twohundred, dependent="geomorphologie_beschreibung", predictors=c("slope_DTM_50m_avg_ws7","Convexity","profc_DTM_50m_avg_ws7","planc_DTM_50m_avg_ws7","maxic_DTM_50m_avg_ws5"),legend=geolegendeng,altdata=onehundred)
```

###SVM n=200
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_localterrain_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full(modeldata=onehundred, dependent="geomorphologie_beschreibung", predictors=c("slope_DTM_50m_avg_ws7","Convexity","Longitudinal_Curvature","slope_ws11","crosc_DTM_50m_avg_ws7"),legend=geolegendeng,altdata=twohundred)
```

### RandomForest n=100
```{r}
importance_ranfor_pset_newlegend(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=2,altdata=twohundred,legend=geolegendeng)
```

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_localterrain_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full(modeldata =onehundred,dependent="geomorphologie_beschreibung",predictors=c("slope_DTM_50m_avg_ws7","profc_DTM_50m_avg_ws7","Convexity","Slope","Total_Curvature","crosc_DTM_50m_avg_ws7"),altdata=twohundred,legend=geolegendeng)
```

### RandomForest n=200,
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_localterrain_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full(modeldata =twohundred,dependent="geomorphologie_beschreibung",predictors=c("slope_DTM_50m_avg_ws7","longc_DTM_50m_avg_ws7","Convexity","crosc_DTM_50m_avg_ws7","slope_ws11"),altdata=onehundred,legend=geolegendeng)
```
##REGIONAL TERRAIN 
### SVM n=100
```{r}
predict_radial_newlegend_fullparamset(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=3,altdata=twohundred,legend=geolegendeng)
```

```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_regionalterrain_100pg/",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full(modeldata=onehundred, dependent="geomorphologie_beschreibung", predictors=c("Channel_Network_Base_Level","Catchment_slope","Topographic_Wetness_Index","Modified_Catchment_Area","LS_Factor","sagaTopographic_Wetness_Index"),legend=geolegendeng,altdata=twohundred)
```
### SVM n=200 
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_regionalterrain_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
```{r,echo=F}
predict_radial_newlegend_full(modeldata=twohundred, dependent="geomorphologie_beschreibung", predictors=c("Channel_Network_Base_Level","Catchment_slope","Topographic_Wetness_Index","Modified_Catchment_Area","LS_Factor","sagaTopographic_Wetness_Index"),legend=geolegendeng,altdata=onehundred)
```

### RandomForest n=100

```{r}
importance_ranfor_pset_newlegend(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=3,altdata=twohundred,legend=geolegendeng)
```

```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_regionalterrain_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full(modeldata =onehundred,dependent="geomorphologie_beschreibung",predictors=c("Channel_Network_Base_Level","Catchment_slope","Topographic_Wetness_Index","RelativeSlopePosition","LS_Factor"),altdata=twohundred,legend=geolegendeng)
```




### RandomForest n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_regionalterrain_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full(modeldata =twohundred,dependent="geomorphologie_beschreibung",predictors=c("Channel_Network_Base_Level","Catchment_slope","Topographic_Wetness_Index","RelativeSlopePosition","LS_Factor"),altdata=onehundred,legend=geolegendeng)
```


##ROUGHNESS
###SVM n=100

```{r}
predict_radial_newlegend_fullparamset(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=5,altdata=twohundred,legend=geolegendeng)
```

```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_roughnesscols_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full_naproblem(modeldata=onehundred, dependent="geomorphologie_beschreibung", predictors=c("TRI_hr_ws26","Texture","fischerk_ws59","terraintexture_hr_ws57_tp25","vectorruggedness_hr_ws59"),legend=geolegendeng,altdata=twohundred)
```

### SVM n=200 
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_roughnesscols_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
```{r,echo=F}
predict_radial_newlegend_full_naproblem(modeldata=twohundred, dependent="geomorphologie_beschreibung", predictors=c("TRI_hr_ws26","Texture","fischerk_ws59","terraintexture_hr_ws57_tp25","vectorruggedness_hr_ws59"),legend=geolegendeng,altdata=onehundred)
```


### RandomForest n=100    

```{r}
importance_ranfor_pset_newlegend(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=5,altdata=twohundred,legend=geolegendeng)
```

```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_roughnesscols_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full_naproblem(modeldata=onehundred,dependent="geomorphologie_beschreibung",predictors=c("TRI_hr_ws24","Texture","vectorruggedness_hr_ws57","vectorstrength_hr_ws59","terraintexture_hr_ws53_tp25"),altdata=twohundred,legend=geolegendeng)
```

### RandomForest n=200
```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_roughnesscols_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full_naproblem(modeldata=onehundred,dependent="geomorphologie_beschreibung",predictors=c("TRI_hr_ws26","Texture","vectorruggedness_hr_ws57","fischerk_ws61","terraintexture_hr_ws53_tp25"),altdata=twohundred,legend=geolegendeng)
```

##RLI
### SVM n=100
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_rlicols_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full_naproblem(modeldata=onehundred, dependent="geomorphologie_beschreibung", predictors=c("geom_hr_L3_fl10_r_li_richness_UE_hr_20cells","geom_hr_L50m_fl1_r_li_edgedensity_UE_hr_20cells","geom_hr_L3_fl10_r_li_dominance_UE_hr_40cells"),legend=geolegendeng,altdata=twohundred)
```
### SVM n=200
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_rlicols_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full_naproblem(modeldata=twohundred, dependent="geomorphologie_beschreibung", predictors=c("geom_hr_L3_fl10_r_li_richness_UE_hr_20cells","geom_hr_L50m_fl1_r_li_edgedensity_UE_hr_20cells","geom_hr_L3_fl10_r_li_dominance_UE_hr_40cells"),legend=geolegendeng,altdata=onehundred)
```

### RandomForest n=100
```{r}
importance_ranfor_pset_newlegend(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=4,altdata=twohundred,legend=geolegendeng)
```

```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_rlicols_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full_naproblem(modeldata =onehundred,dependent="geomorphologie_beschreibung",predictors=c("geom_hr_L3_fl10_r_li_richness_UE_hr_20cells","geom_hr_L3_fl1_r_li_dominance_UE_hr_20cells"),altdata=twohundred,legend=geolegendeng)
```
### RandomForest n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_rlicols_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full_naproblem(modeldata =twohundred,dependent="geomorphologie_beschreibung",predictors=c("geom_hr_L3_fl10_r_li_richness_UE_hr_20cells","geom_hr_L3_fl1_r_li_dominance_UE_hr_20cells"),altdata=onehundred,legend=geolegendeng)
```
## HEIGHTS
### SVM n=100
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_heights_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full_naproblem(modeldata=onehundred, dependent="geomorphologie_beschreibung", predictors=c("Maximum_Height_hr","ValleyDepth","Vertical_Distance_to_Channel_Network","SlopeHeight","Valley_Depth_hr","Normalized_Height"),legend=geolegendeng,altdata=twohundred)
```

### SVM n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_heights_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
```{r,echo=F}
predict_radial_newlegend_full_naproblem(modeldata=twohundred, dependent="geomorphologie_beschreibung", predictors=c("Maximum_Height_hr","ValleyDepth","Vertical_Distance_to_Channel_Network","SlopeHeight","Valley_Depth_hr","Normalized_Height"),legend=geolegendeng,altdata=onehundred)
```

### RandomForest n=100

```{r}
importance_ranfor_pset_newlegend(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=6,altdata=twohundred,legend=geolegendeng)
```
```{r}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_heights_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
with same predictors as svm
```{r}
predict_ranfor_newlegend_full(modeldata =onehundred,dependent="geomorphologie_beschreibung",predictors=c("Maximum_Height_hr","ValleyDepth","Vertical_Distance_to_Channel_Network","SlopeHeight","Valley_Depth_hr","Normalized_Height"),altdata=twohundred,legend=geolegendeng)
```

with own predictors:
```{r}
predict_ranfor_newlegend_full(modeldata =onehundred,dependent="geomorphologie_beschreibung",predictors=c("Vertical_Distance_to_Channel_Network","Maximum_Height_hr","Relative_Slope_Position","Standardized_Height","Slope_Height","ValleyDepth"),altdata=twohundred,legend=geolegendeng)
```

### RandomForest n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_heights_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full(modeldata =twohundred,dependent="geomorphologie_beschreibung",predictors=c("Vertical_Distance_to_Channel_Network","Maximum_Height_hr","Relative_Slope_Position","Standardized_Height","Slope_Height","ValleyDepth"),altdata=onehundred,legend=geolegendeng)
```
## ALLGEOMS
### SVM n=100
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_allgeoms_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r,echo=F}
predict_radial_newlegend_full_naproblem(modeldata=onehundred, dependent="geomorphologie_beschreibung", predictors=c("geom_DTM_50m_avg_fl1_L1500m","geom_DTM_50m_avg_fl10_L150m"),legend=geolegendeng,altdata=twohundred)
```


### SVM n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"svm_fw_5fold_10p_geomorphologie_beschreibung_allgeoms_200pg_v2",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```




```{r,echo=F}
predict_radial_newlegend_full_naproblem(modeldata=twohundred, dependent="geomorphologie_beschreibung", predictors=c("geom_DTM_50m_avg_fl1_L1500m","geom_DTM_50m_avg_fl10_L150m"),legend=geolegendeng,altdata=onehundred)
```
```{r}
importance_ranfor_pset_newlegend(modeldata=onehundred,dependent="geomorphologie_beschreibung",pset=7,altdata=twohundred,legend=geolegendeng)
```
### RandomForest n=100
```{r,echo=F}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_allgeoms_100pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full(modeldata =onehundred,dependent="geomorphologie_beschreibung",predictors=c("geom_DTM_50m_avg_fl1_L1500m","geom_DTM_50m_avg_fl10_L400m"),altdata=twohundred,legend=geolegendeng)
```
Für höchste importance:
```{r}
predict_ranfor_newlegend_full(modeldata =onehundred,dependent="geomorphologie_beschreibung",predictors=c("geom_10m_fl10_L3","geom_DTM_50m_avg_fl10_L200m"),altdata=twohundred,legend=geolegendeng)
```

### RandomForest n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath=paste(base,"ranfor_fw_5fold_10p_geomorphologie_beschreibung_allgeoms_200pg",sep=""),kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

```{r}
predict_ranfor_newlegend_full(modeldata =twohundred,dependent="geomorphologie_beschreibung",predictors=c("geom_DTM_50m_avg_fl1_L1300m","geom_DTM_50m_avg_fl10_L1500m"),altdata=onehundred,legend=geolegendeng)
```





