---
title: "GEOeinheiten Parameterauswahl für 100pergeomorph"
author: "fabian gruber"
date: "April 24, 2017"
output: html_document
---
<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 22px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size:20px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 8px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

      
```{r,include=FALSE}
library(RCurl)
library(rgrass7)
library(repmis)
require(xtable)
myfunctions <- getURL("https://raw.githubusercontent.com/fernstgruber/Rstuff/master/fabiansandrossitersfunctions.R", ssl.verifypeer = FALSE)
eval(parse(text = myfunctions))
source_data("https://github.com/fernstgruber/PROJECTP2/raw/master/data2017/classesandparamsets.RData")
base="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/"
```

##ALL TERRAIN 
### SVM n=100
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/svm_fw_5fold_10p_geomorphologie_beschreibung_allterraincols_100pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### SVM n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/paper2_lenny_JUNE13/data_paper2/data2017/svm_fw_5fold_10p_geomorphologie_beschreibung_allterraincols_200pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=100
```{r,echo=F}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_allterraincols_100pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_allterraincols_200pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

##LOCAL TERRAIN 
###SVM n=100
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/svm_fw_5fold_10p_geomorphologie_beschreibung_localterrain_100pg/",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
###SVM n=200
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/paper2_lenny_JUNE13/data_paper2/data2017/svm_fw_5fold_10p_geomorphologie_beschreibung_localterrain_200pg/",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=100
```{r,echo=F}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_localterrain_100pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_localterrain_200pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```

##REGIONAL TERRAIN 
### SVM n=100
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/svm_fw_5fold_10p_geomorphologie_beschreibung_regionalterrain_100pg/",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### SVM n=200 
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/svm_fw_5fold_10p_geomorphologie_beschreibung_regionalterrain_200pg/",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=100
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_regionalterrain_100pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_regionalterrain_200pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
##ROUGHNESS
###SVM n=100
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/svm_fw_5fold_10p_geomorphologie_beschreibung_roughnesscols_100pg/",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### SVM n=200 
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/paper2_lenny_JUNE13/data_paper2/data2017/svm_fw_5fold_10p_geomorphologie_beschreibung_roughnesscols_200pg/",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=100
```{r,echo=F}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_roughnesscols_100pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=200
```{r,echo=F}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_roughnesscols_200pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
##RLI
### SVM n=100
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/svm_fw_5fold_10p_geomorphologie_beschreibung_rlicols_100pg/",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### SVM n=200
```{r, echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/paper2_lenny_JUNE13/data_paper2/data2017/svm_fw_5fold_4p_geomorphologie_beschreibung_rlicols_200pg/",kk = 1:5,endround = 4,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=100
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_rlicols_100pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```
### RandomForest n=200
```{r,echo=FALSE}
evaluateforwardCV_anyerror(mypath="/media/fabs/Volume/01_PAPERZEUG/newstuff_p2/ranfor_fw_5fold_10p_geomorphologie_beschreibung_rlicols_200pg",kk = 1:5,endround = 10,error = "cverror",geheim="geheimerprederror",yrange=c(0,1))
```